Review: Adaptive Introgression has Expanded the Genetic Base of Crops during post-Domestication Spread

### 2017-06-28 paper.tex
rearranging domestication concepts section

A framework in which crops were domesticated from a single population or even a single species is, in several instances, an oversimplification.
An history of introgression during diffusion appears to be the rule for crops rather than the exception.
Theory suggests that colonizing species will overwhelmingly be recipients of introgression from locally-adapted native species \cite{Currat2008}.
Crops, given their frequent history of diffusion from defined centers of origin, are therefore potential recipients of adaptive introgression.

With this in mind, certain aspects of crop evolution must be re-evaluated:

* Estimates of the initial domestication bottleneck may be skewed when introgression is not considered.
Chromosomal regions experiencing introgression may have an altered effective population size ($N_e$) relative to non-introgressed regions depending on diversity within the donor taxon.
For example, introgression from wild taxa with historically high $N_e$ will lead to underestimates of the strength of the domestication bottleneck.
Conversely, if the donor population has a relatively small effective population size, the opposite bias may be imposed upon bottleneck estimations.
In most cases, the effective population size of the domesticated crop will be lower than that of the wild progenitor and wild relative populations.

* Estimates of the timing of domestication based on levels of sequence divergence may be affected when introgressed haplotypes are included.
The directionality of this effect is likewise dependent on $N_e$ of the donor population.

* Loci under selection during domestication are often identified based on signatures of substantially-reduced nucleotide diversity in the domesticated taxon relative to the wild progenitor and high allele frequency differentiation between these taxa.
Introgression may alter these signatures and confound detection of domestication loci.

@@

* When  highly-introgressed or hybrid populations are selected for domestication (as in the case of potato and tomato), identification of original progenitor(s) and domestication centers is difficult.
Determining whether a crop 
Crops arising from highly-interfertile compleces of wild relatives

>>>>

A framework in which crops were domesticated from a single population or even a single species is, in many instances, an oversimplification.
An history of introgression during geographic expansion increasingly appears to be quite common.
The addition of gene flow to our understanding of crop demography could bear importantly on fundamental questions of crop domestication:

\subsection*{What is the progenitor of a crop?}
When  highly-introgressed or hybrid populations are selected for domestication (as in the case of potato and tomato), identification of original progenitor(s) and domestication centers is difficult.
Determining whether a crop 
Crops arising from highly-interfertile compleces of wild relatives

\subsection*{When was a crop domesticated?}
Estimates of the timing of domestication based on levels of sequence divergence may be affected when introgressed haplotypes are included.
The directionality of this effect is likewise dependent on $N_e$ of the donor population.

\subsection*{How was genome-wide diversity impacted by a domestication bottleneck?}
Estimates of the initial domestication bottleneck may be skewed when introgression is not considered.
Chromosomal regions experiencing introgression may have an altered effective population size ($N_e$) relative to non-introgressed regions depending on diversity within the donor taxon.
For example, introgression from wild taxa with historically high $N_e$ will lead to underestimates of the strength of the domestication bottleneck.
Conversely, if the donor population has a relatively small effective population size, the opposite bias may be imposed upon bottleneck estimations.
In most cases, the effective population size of the domesticated crop will be lower than that of the wild progenitor and wild relative populations.

\subsection*{What candidate genes were targeted by selection during domestication?}
Loci under selection during domestication are often identified based on signatures of substantially-reduced nucleotide diversity in the domesticated taxon relative to the wild progenitor and high allele frequency differentiation between these taxa.
Introgression may alter these signatures and confound detection of domestication loci.

@@
